---
title: "Classification of Heart Disease Within Individuals"
subtitle: "MATH2319 Machine Learning"
author: "Abhishekh Shankar s3652116 & Eric Bolitho s3455890"
output:
  pdf_document:
    fig_caption: yes
    number_sections: yes
    toc: no
    toc_depth: 3
linkcolor: blue
documentclass: article
bibliography: references.bib
---

\newpage

\tableofcontents

\newpage

# Introduction
The objective of this project is to predict whether or not a patient has heart disease indicated as an integer value from 0 to 1 for the absense and presence of heart disease respectively. The dataset was sourced from the UCI Machine Learning Repository [^1] [@heartDisease_uci].

Phase One saw the data being cleaned, with absent values being removed if the total percentage of absent values was under a predefined threshold of 60%, or the entire column being removed if it was over 60%. Phase Two covers model building and analysis with Section Two covering the methodology taken in this phase, Section Three covering ... 

[^1]: https://archive.ics.uci.edu/ml/datasets/Heart+Disease

# Methodology


# Hyperparameter Fine-Tuning

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=TRUE}
library(mlr)
library(tidyverse)
data <- read.csv('cleanHeartData.csv')

# Split into training/testing data.
training_index <- sample(nrow(data)*0.70)
test_index <- setdiff(seq(1:nrow(data)), training_index)

# Get the training and test data.
training_data <- data[training_index, ]
test_data <- data[test_index, ]

# Modelling
task <- makeClassifTask(data = training_data, target = 'num', id= 'X')

# Configure learners with probability type
NB.lrn <- makeLearner('classif.naiveBayes', predict.type='prob') #baseline
RF.lrn <- makeLearner('classif.randomForest', predict.type='prob')
KNN.lrn <- makeLearner('classif.kknn', predict.type='prob')

# KNN
ps1 <- makeParamSet(
  makeDiscreteParam('k', values = seq(2, 20, by = 1))
)



```


## Naive Bayes

## Random Forest

## K-Nearest Neighbours

We read in the data set using the following code.

```{r, out.width='25%', fig.align='center', fig.cap='lel'}


```


# Evaluation

Initially we fit a full regression model using the code snippet below.

```{r}

```


# Discussion


# Conclusion


\newpage

# References

